\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
added citations. Going to read though and cull

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}
\newpage
\section{Introduction}\label{intro}
Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically. At the heart of this progress is the mantra that physical observables are simpler when studied on-shell. However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories. A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors. When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.

However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level. Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}. In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.

We begin by providing background on the duality between color

In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional. This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public. 
 \section{Background}\label{background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}\label{onShellCK}

@@

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes in the product of trees, and
restricting the set of compatible diagrams to those whose color
factors reduce to the appropriate DDM element when summing over
\emph{only the uncut color contractions}.  In this situation, the
color becomes an overall factor on the entire equality and thus can be
ignored.  Cuts that are organized in this manner are known as
``color-ordered'' cuts, in the same sense as color-ordered tree
amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
needs to evaluate that many separate color-orderings of the same cut. \jm{Don't you need $(n-2)!$ for each blob in the cut?  So you need to evaluate $(n_1-2)! (n_2-2)!...$ cuts where $n_1$, $n_2$... are the multiplicities of the blobs.}
As an example, consider the ``kissing triangle'' cut topology -- one of
the factorization channels of the iterated unitarity cut -- which has
two topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
   \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      n\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.

@@

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}\label{2loopBoot}

\subsection{Two-loop NLSM}\label{2loopNLSM}
\label{sec:pions}

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing constraints
that directly involve such pathological diagrams.  That leaves us with
14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
which to impose maximal cuts and symmetries.  Doing so, we are left
with AA total parameters in the unrestricted ansatz and BB total in
the BDN-restricted ansatz.
\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH,
}
  \caption{The 14 non-pathological maximal-cut diagrams} \label{fig:MaxCuts}
  \end{figure}

Proceeding to the next-to-maximal cuts, we continue to avoid
pathological diagrams including the newly-appearing type discussed in
\cref{eq:other-path}.
After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
relations and symmetries.  Interestingly, the ``kissing triangles'' or ``bowtie''
cut,
\begin{equation*}
   \NMCutC \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied. 
\begin{figure}
\centering
 { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
 \\
 \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
  \caption{The 8 non-pathological next-to-maximal-cut diagrams.}
  \label{fig:ym-nmc}
\end{figure}

In fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of
external or loop).  Each ansatz will be 10,010 terms initially.  Next
impose the symmetry constraints on each of the three diagrams, leaving
2761 free parameters on the double-box, 2576 free parameters on the
crossed-box, and 5040 free paramters on the penta-triangle.  Then
impose the ``kissing triangle'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions
from the double-box
\begin{equation}
   \NMCutC
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  n \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang--Mills representation: locality,
symmetry, and the kinematic Jacobi relations for just three diagrams
are incompatible with the ``kissing triangle'' cut.

@@

\mathcal{R}_{m,L} = \frac{P_{b+a}(kk,kl,ll)}{Q_a(kk,kl,ll)}, \qquad b=m+2(l-1)

>>>>

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}
\newpage
\section{Introduction}\label{intro}
Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically. At the heart of this progress is the mantra that physical observables are simpler when studied on-shell. However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell simplicity at the heart of many quantum field theories. A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors. When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.

However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, color-kinematics remains a conjecture at loop level. Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}. In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.

We begin with an overview of color-kinematics duality in \cref{background}. We then construct a manifestly color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point numerators for both NLSM and the self-dual sector of Yang-Mills through one-loop. The construction of this theory, which we dub \textit{semi-abelian Yang-Mills}, relies on isolating the cubic sector of pure Yang-Mills amplitudes from the four-point contacts that are needed to fully realize non-abelian gauge symmetry. Despite the potency of this theory at one-loop, the construction runs into an obstruction at two-loop, which we describe in \cref{2LoopObstruction}.

Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap. In contrast to much of the available literature on construction of color-dual integrands at two-loop \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional. This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta. We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.

With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell. This represents a new benchmark for color-dual representations in non-supersymmetric gauge theories. However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation, even when considering the most general polynomial ansatz of Lorentz covariant kinematics. Concretely, we find a sharp failure point between the ``bowtie'' cut, and the following jacobi triple:
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one must relax field theoretic locality in order to accommodate the construction of globally color-dual multi-loop integrands.

\section{Background}\label{background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then detail a color-dual boostrap approach for constructing integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}\label{onShellCK}

@@

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes in the product of trees, and
restricting the set of compatible diagrams to those whose color
factors reduce to the appropriate DDM element when summing over
\emph{only the uncut color contractions}.  In this situation, the
color becomes an overall factor on the entire equality and thus can be
ignored.  Cuts that are organized in this manner are known as
``color-ordered'' cuts, in the same sense as color-ordered tree
amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
needs to evaluate that many separate color-orderings of the same cut. \jm{Don't you need $(n-2)!$ for each blob in the cut?  So you need to evaluate $(n_1-2)! (n_2-2)!...$ cuts where $n_1$, $n_2$... are the multiplicities of the blobs.}
As an example, consider the ``bowtie'' cut topology -- one of
the factorization channels of the iterated unitarity cut -- which has
two topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
   \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      n\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.

@@

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}\label{2loopBoot}
We now employ the color-dual bootstrap method described in \cref{bootstrap}. We will employ an ansatz constructed from  $D$-dimensionally Lorentz covariant kinematics. To fix remaining freedom in the NLSM bootstrap, we will match down to ZM theory in $D=2$. This is merely an aesthetic choice, so the final results of both the NLSM and Yang-Mills bootstraps are dimensionally agnostic.
\subsection{Two-loop NLSM}\label{2loopNLSM}
\label{sec:pions}

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing constraints
that directly involve such pathological diagrams.  That leaves us with
14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
which to impose maximal cuts and symmetries.  Doing so, we are left
with AA total parameters in the unrestricted ansatz and BB total in
the BDN-restricted ansatz.
\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH,
}
  \caption{The 14 non-pathological maximal-cut diagrams, including all dangling tree diagrams.} \label{fig:MaxCuts}
  \end{figure}

Proceeding to the next-to-maximal cuts, we continue to avoid
pathological diagrams including the newly-appearing type discussed in
\cref{eq:other-path}.
After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
relations and symmetries.  Interestingly, the ``bowtie'' or ``kissing-triangles''
cut,
\begin{equation*}
   \NMCutC \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied. 
\begin{figure}
\centering
 { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
 \\
 \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
  \caption{The 8 non-pathological 1-particle-irreducible next-to-maximal-cut diagrams used in our cut constraints on the Yang-Mills integrand.}
  \label{fig:ym-nmc}
\end{figure}

In fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of
external or loop).  Each ansatz will be 10,010 terms initially.  Next
impose the symmetry constraints on each of the three diagrams, leaving
2761 free parameters on the double-box, 2576 free parameters on the
crossed-box, and 5040 free paramters on the penta-triangle.  Then
impose the ``bowtie'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions
from the double-box
\begin{equation}
   \NMCutC
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  n \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang--Mills representation: locality,
symmetry, and the kinematic Jacobi relations for just three diagrams
are incompatible with the ``bowtie'' cut.

@@

\mathcal{R}_{m,L} = \frac{P_{b+a}(k^2,kl,l^2)}{Q_a(k^2,kl,l^2)}, \qquad b=m+2(l-1)
